---
title: "methods@manchester: API intro"
author: "Renata Topinkova"
date: "14 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load libraries
```{r libs}
#install.packages("package_name")

library(httr)
library(dplyr)
``` 


## Query API
API: https://api.nationalize.io
Parameters are organized as key - value pairs. See the allowed parameters in the API documentation.

```{r endpoints}
# Specify the endpoint
endpoint <- "https://api.nationalize.io?"


# Query the API
req <- GET(endpoint, 
           # specify the parameters for your query
           query = list(
             name = "Renata"
           ))

# Alternatively: GET("https://api.nationalize.io?name=renata")

# Explore what we've collected
req

```
--> Status 200 - ok, query successful


### Parsing the content of our query
To parse the content of the API query, we need the `content` function from the `httr` package.
`content` function has `as` argument that specifies how the content will be parsed (`raw`, `text`, `parsed`). 
If you do not specify the argument, R will make its best guess to parse the data. Sometimes it's accurate, sometimes not - you can play around with it.

Alternatively, you can parse json content with `jsonlite` package.

```{r}
# See the content of the query
content(req)

# Play around with the parsing
content(req, "text") # js notation
content(req, "raw") # not human-readable
content(req, "parsed") # best version - list

```

## Your turn!

### 1.1. Query: Your name.
Query the Nationalize.io API (https://api.nationalize.io) to predict the nationality of your name. 
```{r}

```



### 1.2. Query Genderize.io I: Name
Look up the documentation for a new API https://genderize.io/
Query the API to predict the gender for the name "Jessie".
```{r}

```


### 1.3. Query Genderize.io II: Name & Country
Query the API https://genderize.io/ to predict the gender for the name "Jessie" in the US and the UK. Is there any difference? 
You will have to submit two queries.
Hint: Look up the country codes in `our data`. 
```{r}

```



