---
title: "methods@manchester: API intro: Omdb API"
author: "Renata Topinkova"
date: "15 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
```{r libs}
library(httr)
library(dplyr)
``` 




## Endpoint & apikey
Get to the Omdb API website: https://www.omdbapi.com/
- Apply for a free API token: https://www.omdbapi.com/apikey.aspx
  - Select Account type: Free
- Once you receive your API key via email, enter it into the endpoint in place of #### in the code

**Note:** As a best practice, you should not be hardcoding your API tokens into your code. Instead, it is better to make use of R environments. 
More on this: https://bookdown.org/paul/apis_for_social_scientists/best-practices.html

```{r endpoints}
## Replace #### with the token you have received via email
endpoint <- "http://www.omdbapi.com/?apikey=####"

```




## Your turn!

### ### 1. Find out which movie has id "tt0425112"
```{r}

```



### 2. Get the full plot of the mystery movie that from ex. 1 
```{r}

```

### 3. Find movies that have "dog" in their title. 
Note: There should be more than one. 
```{r}

```

### BONUS 1: Get more "dog" movies. 
Hint: Look into the documentation. Which parameter you could use to get additional results? 
```{r}

```


### BONUS 2: Bind the results from exercise 3 (and optionally, also Bonus 1) into a dataframe (tibble)
There are many solutions from different packages (base, dplyr, tidyr, purrr), don't be afraid to experiment!
```{r}

```

