---
title: "methods@manchester: API intro: Omdb API solutions"
author: "Renata Topinkova"
date: "15 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
```{r libs}
library(httr)
library(dplyr)
``` 




## Endpoint & apikey
Get to the Omdb API website: https://www.omdbapi.com/
- Apply for a free API token: https://www.omdbapi.com/apikey.aspx
  - Select Account type: Free
- Once you receive your API key via email, enter it into the endpoint in place of #### in the code

**Note:** As a best practice, you should not be hardcoding your API tokens into your code. Instead, it is better to make use of R environments. 
More on this: https://bookdown.org/paul/apis_for_social_scientists/best-practices.html

```{r endpoints}
## Replace #### with the token you have received via email
endpoint <- "http://www.omdbapi.com/?apikey=####"

```




## Your turn!

### 1. Find out which movie has id "tt0425112"
```{r}
mystery_movie <- GET(endpoint, 
                     query = list(i = "tt0425112"))

# status ok
mystery_movie

# content
content(mystery_movie)

```



### 2. Get the full plot of the mystery movie that from ex. 1 
```{r}
plt_movie <- GET(endpoint,
                 query = list(
                  i = "tt0425112",
                  plot = "full" ))

# response
plt_movie

# parse content
plt_movie_full <- content(plt_movie)

# show plot
plt_movie_full$Plot
```

### 3. Find movies that have "dog" in their title. 
Note: There should be more than one. 
```{r}
dog <- GET(endpoint, 
           query = list(s = "dog"))

df_dog <- content(dog)

bind_rows(df_dog$Search)
```

### BONUS 1: Get more "dog" movies. 
Hint: Look into the documentation. Which parameter you could use to get additional results? 
```{r}
# omdb returns 10 results per page --> page = 2 gives different results than page = 1 (default)
dog_p2 <- GET(endpoint, 
              query = list(
                s = "dog", 
                page = 2))
dog_p2
content(dog_p2)

df_dog2 <- content(dog_p2)
## This is useful for automatization of the data collection - we can iterate over the page numbers (i)
```


### BONUS 2: Bind the results from exercise 3 (and optionally, also Bonus 1) into a dataframe (tibble)
There are many solutions from different packages (base, dplyr, tidyr, purrr), don't be afraid to experiment!
```{r}
bind_rows(df_dog$Search, df_dog2$Search)
```

