---
title: "methods@manchester: API intro"
author: "Renata Topinkova"
date: "14 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load libraries
```{r libs}
#install.packages("package_name")

library(httr)
library(dplyr)
``` 


## Query API
API: https://api.nationalize.io
Parameters are organized as key - value pairs. See the allowed parameters in the API documentation.

We can query the API with `GET` function from `httr`package. 
`GET` function requires the endpoint of the API, and the query (key = value pairs) which has to be inside a `list`. 

Alternatively, you can simply write your query as a string. This is fine for short queries but may create problems when your queries become more complex (i.e., when you use more parameters). 

```{r endpoints}
# Specify the endpoint
endpoint <- "https://api.nationalize.io?"



# Query the API
req <- GET(endpoint, 
           # specify the parameters
           query = list(
             name = "Renata"))

# Alternatively, you can get the same results with: GET("https://api.nationalize.io?name=renata")

# Explore what we've collected
req

```
--> Status 200 - ok, query successful


### Parsing the content of our query
To parse the content of the API query, we need the `content` function from the `httr` package.
`content` function has `as` argument that specifies how the content will be parsed (`raw`, `text`, `parsed`). 
If you do not specify the argument, R will make its best guess to parse the data. Sometimes it's accurate, sometimes not - you can play around with it.

Alternatively, you can parse json content with `jsonlite` package.

```{r}
# See the content of the query
content(req)

# Play around with the parsing
content(req, "text") # js notation
content(req, "raw") # not human-readable
content(req, "parsed") # best version - list

```

## Your turn!

### 1.1. Query: Your name.
Query the Nationalize.io API (https://api.nationalize.io) to predict the nationality of your name. 
```{r}
petra <- GET(endpoint, 
             query = list(
              name = "Petra"))

petra

content(petra)
```


### 1.2. Query Genderize.io I: Name
Look up the documentation for a new API https://genderize.io/
Query the API to predict the gender for the name "Jessie".
```{r}
endpoint_gndr <- "https://api.genderize.io?"
jessie <- GET(endpoint_gndr,
              query = list(
                name = "Jessie"
              ))
content(jessie)
```


### 1.3. Query Genderize.io II: Name & Country
Query the API https://genderize.io/ to predict the gender for the name "Jessie" in the US and the UK. Is there any difference? 
You will have to submit two queries.
Hint: Look up the country codes in `our data`. 
```{r}
# Get the predictions for the US
jessie_us <- GET(endpoint_gndr,
  query = list(
    name = "Jessie",
    country_id = "US"
  )
)
content(jessie_us)


# Get the predictions for the UK
jessie_gb <- GET(endpoint_gndr,
  query = list(
    name = "Jessie",
    country_id = "GB"
  )
)

content(jessie_gb)

```



## Additional material: Data wrangling

### Wrapping the output into a dataframe (example we have done together)
```{r}
# use the parsed API response
content(req, "parsed") %>%
  # convert it to tibble
  as_tibble() %>%
  # unnest the country column
  tidyr::unnest_wider(country)
```


### Wrapping the output into a dataframe (ex. 1.3)
```{r}
list(content(jessie_us), content(jessie_gb)) %>%
  # convert to data frame
  purrr::map_df(as.data.frame)
  
```

