---
title: "methods@manchester: Screenscraping - Quotes to scrape: Solutions"
author: "Renata Topinkova"
date: "14 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load libraries
```{r}
library(rvest)
library(dplyr)
```


## Read the webpage into R
In this exercise, we are working with https://quotes.toscrape.com
```{r}
page <- read_html("https://quotes.toscrape.com")
page
```


## Your turn!

### 1. Extract the texts of quotes
```{r}
quotes <- html_elements(page, ".text") %>%
  html_text()

quotes
```


### 2. Extract the authors of the quotes
Note: The number of authors should correspond to the number of quotes
```{r}
authors <- html_elements(page, ".author") %>%
  html_text()

authors
```


### 3. Bind the quotes and their authors into a dataframe
Note: Think about functions you know from base R, dplyr, or other packages you use.
```{r}
df <- tibble(text = quotes, author = authors)
```

### 4. Bonus: Extract links to authors' pages
Note: You will need `html_attr()` to do it. 
```{r}
urls <- html_elements(page, ".quote span a") %>%
  html_attr("href")

urls


# Bonus to a bonus -> change relative paths to absolute paths
urls <- paste0("https://quotes.toscrape.com", urls)

```


